---
title: 'STA 111: Lab 1'
author: your name
date:
output: pdf_document
---

```{r setup, include=FALSE}
# DO NOT ALTER CODE IN THIS CHUNK
knitr::opts_chunk$set(echo = TRUE)
```

* * *
#### 1: 
This is an R Markdown lab report template. 
Before we get started, let's save this file to the same folder where the data is stored. 
You can embed an R code chunk like this:

```{r chunk_name, fig.height=5, fig.width=5, fig.align="center"}
load("cdc.RData")

hist(cdc$age, breaks=30, col="lightblue")
# code for Exercise 1
```

Try clicking the **Knit** button and a pdf document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

You can specify the height and width of the figure generated through `fig.height` and `fig.width`.

Enter your response for Exercise 1.

#### 2:

```{r, echo=FALSE}
# enter your code for Exercise 2 here
```

You can add `echo = FALSE` to the code chunk to prevent printing of the R code. Sometimes you may need `message=FALSE` to suppress any R warnings or messages from being included in the final document.

Enter your response for Exercise 2.

You can use ordered list like

1. item 1
2. item 2
    + sub-item

or unordered list like

* item 1
* item 2
    + sub-item

#### 3:

```{r, results='hide'}
summary(cdc)
# enter your code for Exercise 3 here
```

Conversely, you may want to see the code, but not the output once the code is evalutated. To do so, you can add `results='hide'`.

To include a chunk that is evaluated, but neither the code nor the results are displayed, you can add `include=FALSE`.


